PK object batch mode trial

### 2023-06-20 data-raw/batchMode_trial_gpm.Rmd
Updated RMSE method for faceted data structure

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% "DTXSID0020442")

@@

my_coefs_update <- coef(my_pk, drop_sigma = TRUE)
my_pred_update <- predict(my_pk,
                          use_scale_conc = TRUE)

>>>>

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                                   "DTXSID2021731"))

@@

my_coefs_update <- coef(my_pk)
my_pred_update <- predict(my_pk,
                          exclude = TRUE, # add the "exclude" column to output
                          use_scale_conc = TRUE)

my_ndf <- my_pk$data

rmse(my_pk) %>% View("RMSE_test")
